On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2024-01-08 Manuscript/manuscript.tex
faceted overlaid graphs

One of the goals of this study was to provide some practical recommendations for 
necessary sample sizes when using block bootstrap to estimate parameters of 
serially dependent data. When using Student's $t$ intervals and the marginal
distribution and temporal dependence is 
unknown, the results of this study suggest that $n \geq 1600$ may be necessary 
for common practice to estimate $\mu$, whereas $n > 3200$ may be necessary
to estimate the standard deviation. If 
the dependences tructure or the marginal distribution is already known, a 
lesser $n$ may be 
adequate to estimate these 
parameters. For lower absolute values of $\phi$, a smaller $n$ is sufficient 
when estimating the standard deviation. For negative values of $\phi$, coverage of all 
parameters is higher in general. Under a marginal standard normal distribution, 
Student's $t$ seems to over-cover 
$\mu$ for $\phi = - 0.4$  when 
using smaller sample sizes, meaning that if $\phi$ 
is known to have a very negative value, another CI may be required. However, in 
real world applications, $\phi$ is more commonly found to be positive, so 
Student's $t$ should still be used if $\phi$ is unknown. 
Lastly, to estimate 
$\phi$, $n \geq 100$ using the Student's $t$ method may be sufficient under
a marginal standard normal distribution, whereas $n \geq 1600$ may be required
under under a marginal exponential distribution. Further
investigation may be necessary to see if there are other percentile-based 
interval corrections
that fix the coverage deterioration problem for~$\phi$.
\jy{add tilde to avoid line break where you are sure you don't want a
  line break.}

@@

Based on \textbf{Figure~\ref{fig:mu2}}, for negative autocorrelations, the 
coverage 
rates of $\mu$ appear to be lower when
using $l = \lceil 2n^{1/3} \rceil$. For example, whereas $n = 100$ or 200 
would seem sufficient for most CIs when using $l = \lceil n^{1/3} \rceil$, 
$n = 800$ or 1600 is necessary to capture negative autocorrelations for 
$l = \lceil n^{1/3} \rceil$. Student's $t$ CIs do not seem to be as affected
by this change in $l$: for $\phi = -0.4$ and -0.2, they still over-cover $\mu$
for smaller values of $n$.

\textbf{Figure~\ref{fig:sigma2}} looks very similar to 
\textbf{Figure~\ref{fig:sigma1}}, but coverage rates of $\sigma_x$ do look 
slightly lower
especially for negative values of $\phi$, although Student's $t$ CIs are again
not as influenced by this change in $l$. A larger sample size seems necessary
when using other CIs to estimate $\sigma_x$ for $l = \lceil 2n^{1/3} \rceil$.

>>>>

One of the goals of this study was to provide some practical recommendations for 
necessary sample sizes when using block bootstrap to estimate parameters of 
serially dependent data. When using Student's $t$ intervals and the marginal
distribution and temporal dependence is 
unknown, the results of this study suggest that $n \geq 1600$ may be necessary 
for common practice to estimate $\mu$, whereas $n > 3200$ may be necessary
to estimate the standard deviation. If 
the dependences tructure or the marginal distribution is already known, a 
lesser $n$ may be 
adequate to estimate these 
parameters. For lower absolute values of $\phi$, a smaller $n$ is sufficient 
when estimating the standard deviation. For negative values of $\phi$, coverage of all 
parameters is higher in general. Under a marginal standard normal distribution, 
Student's $t$ seems to over-cover 
$\mu$ for $\phi = - 0.4$  when 
using smaller sample sizes, meaning that if $\phi$ 
is known to have a very negative value, another CI may be required. However, in 
real world applications, $\phi$ is more commonly found to be positive, so 
Student's $t$ should still be used if $\phi$ is unknown. 
Lastly, to estimate 
$\phi$, $n \geq 100$ using the Student's $t$ method may be sufficient under
a marginal standard normal distribution, whereas $n \geq 1600$ may be required
under under a marginal exponential distribution. Further
investigation may be necessary to see if there are other percentile-based 
interval corrections
that fix the coverage deterioration problem for~$\phi$.
\jy{add tilde to avoid line break where you are sure you don't want a
  line break.}
\mc{addressed}

@@

Based on \textbf{Figure~\ref{fig:mu2}}, for negative autocorrelations, the 
coverage 
rates of $\mu$ appear to be lower when
using $l = \lceil 2n^{1/3} \rceil$. For example, whereas $n = 100$ or 200 
would seem sufficient for most CIs when using $l = \lceil n^{1/3} \rceil$, 
$n = 800$ or 1600 is necessary to capture negative autocorrelations for 
$l = \lceil n^{1/3} \rceil$. Student's $t$ CIs do not seem to be as affected
by this change in $l$: for $\phi = -0.4$ and -0.2, they still over-cover $\mu$
for smaller values of~$n$.

\textbf{Figure~\ref{fig:sigma2}} looks very similar to 
\textbf{Figure~\ref{fig:sigma1}}, but coverage rates of $\sigma_x$ do look 
slightly lower
especially for negative values of $\phi$, although Student's $t$ CIs are again
not as influenced by this change in~$l$. A larger sample size seems necessary
when using other CIs to estimate $\sigma_x$ for $l = \lceil 2n^{1/3} \rceil$.

### 2024-01-08 Manuscript/reply.tex
faceted overlaid graphs

Thank you for this idea. We have provided Figure~\ref{fig:mu} as an 
example of what this suggested figure
would look like.

\jy{Could you put the three plots in one? Perhaps use facet grid: phi
  by parameter (mu, sigma, phi). Then we just need one caption.}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/alt_plot_norm_mu_1}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal mean $\mu$ of an AR(1) process with a marginal standard 
    normal distribution with AR coefficient
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. The
    error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:mu}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/alt_plot_norm_sigma_1}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal mean $\sigma$ of an AR(1) process with a marginal standard 
    normal distribution with AR coefficient
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. The
    error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:sigma}
\end{figure}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/alt_plot_norm_phi_1}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal mean $\phi$ of an AR(1) process with a marginal standard 
    normal distribution with AR coefficient
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. The
    error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:phi}
\end{figure}

We find that this format
is a little
cluttered to make comparisons, so we have elected to remain with the original 
format.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/alt2plot_norm_phi_1}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for 
    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
    a marginal standard normal distribution with 
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates of
    block bootstrap with $l = \lceil n^{1/3} \rceil$. The
    error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:alt_phi1}
\end{figure}

\jy{I'm interested in seeing the figures overlaid as in
  Figure~\ref{fig:mu}.}
\mc{addressed}\jy{Put them overlaid; three plots in one with facet
  grid as the last one.}

>>>>

Thank you for this idea. We have provided Figure~\ref{fig:norm1} as an 
example of what this suggested figure
would look like.

\jy{Could you put the three plots in one? Perhaps use facet grid: phi
  by parameter (mu, sigma, phi). Then we just need one caption.}
\mc{I think it looks good, only problem is I'm not sure how friendly it is for
colorblind people. I used a palette which is supposed to be more colorblind
friendly}

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/alt_plot_norm1}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal mean $\mu$, the marginal standard deviation $\sigma_x$, and
    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
    a marginal standard 
    normal distribution with AR coefficient
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. The
    error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:norm1}
\end{figure}

%We find that this format
%is a little
%cluttered to make comparisons, so we have elected to remain with the original 
%format.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=\textwidth]{figures/alt2_plot_norm1}
  \caption{Empirical coverage rates of different 95\% block bootstrap CIs for
    the marginal mean $\mu$, the marginal standard deviation $\sigma_x$, and
    the first-order autocorrelation coefficient $\phi$ of an AR(1) process with 
    a marginal standard 
    normal distribution with AR coefficient
    $\phi \in \{-0.4, 0.2, 0, 0.2, 0.4\}$ and series length
    $n \in \{100, 200, 400, 800, 1600, 3200\}$ based on 10,000 replicates. The
    error bars represent 95\% CIs of the real coverage rates.}
  \label{fig:alt2_norm1}
\end{figure}

\jy{I'm interested in seeing the figures overlaid as in
  Figure~\ref{fig:mu}.}
\mc{addressed}\jy{Put them overlaid; three plots in one with facet
  grid as the last one.}
  \mc{addressed. I think the last one looks better}
